---
output: github_document
---

# Purpose

Purpose of this work folder.

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
library(RColorBrewer)
library(xtable)
library(lubridate)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
covid_data <- read.csv("/Users/gracegrant/Documents/Postgrad/Masters/Data Science/Take home exam/Question 1/data/Covid/owid-covid-data.csv")
deaths_by_cause <- read.csv("/Users/gracegrant/Documents/Postgrad/Masters/Data Science/Take home exam/Question 1/data/Covid/Deaths_by_cause.csv")
description <- read.csv("/Users/gracegrant/Documents/Postgrad/Masters/Data Science/Take home exam/Question 1/data/Covid/covid_data_description.csv")
```
\newpage
# Question 1: COVID
1.1 It might be interesting to look at vaccinations in Africa and the outbreak of the pandemic compared to other regions. For this question I could maybe also look at the deaths by cause database to see how COVID deaths differed to deaths before COVID.
```{r bar deaths}

total_deaths_per_continent <- df_cleaned %>% group_by(location) %>% mutate(total_deaths = total_deaths / 1000000) %>%
  summarise(total_deaths = sum(total_deaths)) 

rm(continent_covid)
rm(df_subset)
rm(bar_deaths)
rm(covid_updated)
rm(df_cleaned)
rm(g)
rm(plot_total_deaths_per_continent)

covid_cleaned <- covid_data %>%
  filter(location %in% c("Africa", "Asia", "North America", "Oceania", "South America", "Europe")) %>% mutate(total_deaths = ifelse(is.na(total_deaths), 0, total_deaths))

covid_cleaned <- covid_cleaned %>% mutate(total_cases = ifelse(is.na(total_cases), 0, total_cases))

bar_deaths <- plot_deaths(covid_cleaned)
bar_deaths
```
This first graph shows the total number of deaths (in millions) for each continent from COVID.

```{r}
library(lubridate)
library(dplyr)
rm(monthly_cases)
rm(covid_data_2020)

suppressWarnings(line_cases <- plot_cases(covid_cleaned))
line_cases
```
This graph shows how each continent experienced a growth in total cases (in millions) in 2020.